% resume.tex

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{enumitem}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\def\labelitemiii{$\bullet$}
\def\labelitemiv{--}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Brett Jurgens}}

297 Plum Drive\ \ \textbullet
\ \ Marlboro, NJ 07746
\\
(732) 858-1540\ \ \textbullet
\ \ brett@brettjurgens.com\ \ \textbullet
\ \ brettjurgens (GitHub)
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Uncorkd, Inc.}}
		{\textbf{Chicago, IL}}
	\\
	\headerrow
		{\emph{Software Development Intern \ -- \ http://www.uncorkd.biz}}
		{\emph{June-August 2013}}
	\begin{itemize*}
		\item Gained experience with CodeIgniter (PHP), Javascript, D3.js, and CSS
		\item Redesigned the company logo and instituted a site-wide design change with a modern design language
		\item Built an "analytics dashboard" with visualization powered by D3.js
		\item Built a web version of the company's mobile app
		\item Actively tested and fixed bugs throughout the site
	\end{itemize*}
	
	\item
	\headerrow
		{\textbf{Gift Finder, Inc.}}
		{\textbf{New York, NY}}
	\\
	\headerrow
		{\emph{Software Development Intern \ -- \ http://www.giftfinder.com}}
		{\emph{June-August 2012}}
	\begin{itemize*}
		\item Gained experience with CakePHP, CoffeeScript, Ruby on Rails, and Sass
		\item Worked with mockups made in Adobe Illustrator to build the website's 
		front-end
	\end{itemize*}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Project Experience}
\begin{description}[leftmargin=0pt]
	\parskip=0.1em
      
      \item[CS 465 Final Project]\hfill\\
      We developed a mobile application which allows a user to crowdsource 
      decisions and gather feedback from friends by sending them a picture. 
      Users are able to view the results in an easy to understand manner.
      
      \item[CS 498STK Final Project]\hfill\\
      For our final project we developed a mobile website to allow a user to 
      create a "trip," invite other users and collect location data on the way. 
      Users can also send each other realtime messages and share their 
      trip online after its completion.
      
	\item[Chambana Bus] {\emph{http://www.chambanabus.com}}\hfill\\
      Website which allows the user to plan trips, find closest stops (using HTML5 
	Geolocation), and more for the local bus service.

	\item[MovieAggregator] {\emph{http://www.movieaggregator.com}}\hfill\\
      Hackathon project to aggregate data from 6 different movie-focused 
      websites, including IMDB, Amazon, Rotten Tomatoes, iTunes, TheMovieDB, and 
      Netflix. Displays important details about the user-requested film, 
      computed rating, and its availability to stream on Netflix or buy on 
      iTunes and Amazon.

	\item[BatchDefine] {\emph{http://www.batchdefine.com}}\hfill\\
      Website created in High School to allow a user to input a list of words 
      and receive the definitions in an organized, save-able, and exportable list. 
      It makes use of Dictionary.com's API to gather the definitions and 
      Facebook's OpenGraph API to share actions to Facebook.

	
\end{description}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{University of Illinois at Urbana-Champaign}}
		{\textbf{Urbana, IL}}
	\\
	\headerrow
		{\emph{College of Engineering, B.S. Computer Science}}
		{\emph{August 2011 -- May 2015 (expected)}}
	\begin{itemize*}
		\item Organizations:
		\begin{itemize}
		  \item Pi Kappa Phi Fraternity
		  \begin{description}
		    \item[Social Internal Chair] In charge of running all internal social 
		    events (formals, date events, etc.)
		    \item[Historian] Executive Council position in charge of Alumni and Parental 
		    Relations.
		    \item[Standards Board Justice] Responsible for upholding the standards of 
		    the organization.
		  \end{description}
		  \item IEEE
		  \item ACM
		\end{itemize}
		\item Relevant Courses:
		
		Introduction to Computer Science, Discrete Structures, Data Structures and 
		Programming Principles, Computer Architecture, Systems Programming, 
		The Art and Science of Web Programming, Theory of Computation, 
		User Interface Design
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Skills and Interests}

\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
       C/\CPP, CSS/Sass, HTML/Haml, Java, Javascript/CoffeeScript, \LaTeX, MySQL, PHP, Python, Ruby
	\item[Services:]
	Amazon Web Service, Google App Engine, Heroku
	\item[Frameworks & Libraries:]
	Android SDK, CakePHP, CodeIgniter, Facebook SDK, Flask, jQuery, Ruby on Rails, Sinatra, webapp2
	\item[Graphic Design:]
	Adobe Illustrator, Adobe Photoshop, UI \& Web Design
	\item[Interests:]
	Android, Databases, Human Computer Interaction \& User Interface Design, Web 
	Applications
\end{description*}

\end{document}
